\RequirePackage[hyphens]{url}
\documentclass[sigconf]{acmart}

\input{format/i523}

\begin{document}

\title{BigchainDB: A Big Database for the Blockchain?}
\author{Timothy A. Thompson}
%\orcid{0000-0001-6574-9010}
\affiliation{%
  \institution{Indiana University Bloomington}
  \streetaddress{School of Informatics, Computing, and Engineering}
  \city{Bloomington} 
  \state{Indiana} 
  \postcode{47408}
}
\email{timathom@indiana.edu}

\begin{abstract} 
Decentralized systems such as Bitcoin, the Interplanetary File System (IPFS), and Ethereum have been designed with the intention of reengineering the architecture of online information systems, of minimizing exposure through centralized points of failure, and of creating new social models for the exchange of data---which is posited as a valuable asset in and of itself. Are these kinds of systems also able to support big data analytics and processing? If so, what stands to be gained by taking a blockchain-based approach to big data? Efforts to integrate blockchains into big data pipelines must inevitably address the tradeoff between security and scalability. BigchainDB is a new decentralized database framework that adds blockchain-based features, such as immutability and secure asset management, to traditional NoSQL distributed databases. Although it is still in the early stages of development, BigchainDB promises to make a significant contribution to the ways in which data is shared, processed, and managed at scale.
\end{abstract}

\keywords{i523, HID340, Decentralization, Databases, NoSQL, Blockchains, BigchainDB}

\maketitle

\section{Introduction}

\section{Distributed versus Decentralized}

\subsection{Tradeoffs between Security and Scalability}
Security and scalability \cite{aA17, bigDB16, bigDB17a, bigDB17b, jC17, kB16, kC16, nM15, tMAI17, tMBD16, sR16}.


\subsection{Blockchains for Big Data}

\section{BigchainDB}

\section{Conclusion}

\begin{acks}
The author would like to thank Dr. Gregor von Laszewski and the i523 teaching assistants for their support and suggestions in writing this paper.
\end{acks}

\bibliographystyle{ACM-Reference-Format}
\bibliography{report} 

\end{document}
